---
title: "linear model from Web"
author: "Estevan Green"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

# Introduction
We predict a stimulated strength based on a arm and grip strength. We will find three models and compare them. The response variable is numerical, so we use the 
num~num helper file.

## Model 1 SIM~ARMS

## Results

### Graphical results

```{r}
mode1.1 <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(mode1.1, col='red')
```
This graph shows that as arm strength increases, the simulation follows.

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation is 0.68 which is showing the arm strength is related to the 
sim score.

## Interfential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
We reject the null hypothesis,because both the intecept and coefficient of ARM strength are both significantly 
different than 0.

### Prediction Interval

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval="predict")
```
The 95% prediction interval is from -1.7 to 3.1 for sim score.

## Model 2 SIM~GRIP

## Results

### Graphical results

```{r}
mode1.2 <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(mode1.2, col='red')
```
The scatter plot shows as the number in grip strength score increases, the 
simulated strength  score increases.
### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation is 0.64, which shows that grip strentgh is related to simulated
strength score.

### Inferential Results (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
``` 
Based on the results , I reject the null hypothesis because the p-value is to small as show in the numbers above.


#### Prediction Interval
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.2, newdata, interval="predict")
```

The 95% prediction interval is from -3.1 to 2.0.


#### now add the model fit to our plot for model.2

  

## Model 3 SIM~ARM+GRIP

## Results


### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```



### Inferential Results

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
``` 

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
```


As arm + grip strength goes up the simulation indicates that the sim goes up as well, we reject the null hypothesis because the p-value is so small.Both coefficients are significant.

#### Prediction Interval
  
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.3, newdata, interval="predict")
```



## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

```{r}
anova(model.1, model.3)
```
 The p-value is .000000049, so we reject the null hypotheis.
```{r}
anova(model.2, model.3)
```

Model 3 is smaller than model 2 because the RSS for model 3 is smaller. 



# Discussion and Conclusion

All in all, model 3 is the best because it has a smaller RSS than both model 1 and model 2. Model 1 is better than model 2, but in order for it to be better, it would need a smaller RSS. In the end, we are rejecting the null hypothesis and model 3 is the best overall.







